Quantifying the importance of an inference model in Bayesian phylogenetics

### 2020-03-26 supplement.tex
Second round of processing feedback from reviewers
Changes @Giappo
Supplementary material complete

@@

\richel{Issue \url{https://github.com/richelbilderbeek/pirouette_article/issues/89}}

This subsection extends the main example, by using multiple (instead of
one) trees. These trees are produced by running a DD tree simulation
with the same parameters as the main example, which are
speciation rate \richel{?}, extinction rate $0.1$, and carrying
capacity 40.

@@

\richel{Issue at \url{https://github.com/richelbilderbeek/pirouette_article/issues/63}}

The main example uses \richel{?} taxa.
One expects that the more taxa are present in a phylogeny,
the better the inference will be, 
thus the lower the errors will be.
Here, we show the same results as the main example,
except for a varying number of taxa.

Note that, \richel{[some authors]} found that an increase in the number
of taxa may counterintuitively decrease the inference.

The code used in this part of the article can be found at 
\url{https://github.com/richelbilderbeek/pirouette_example_20}.

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_20/errors_5.png}
  \caption{5 taxa}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_20/errors_10.png}
  \caption{10 taxa}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_20/errors_20.png}
  \caption{20 taxa}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_20/errors_30.png}
  \caption{30 taxa}
\end{figure}

@@

The main example uses a DNA alignment length of 1000 nucleotides.
One expects that the more nucleotides are present in the alignment,
the more information is available,
thus the better the inference will be, 
thus the lower the errors will be.
Here, we show the same results as the main example,
except for a varying DNA alignment sequence length.

The code used in this part of the article can be found at 
\url{https://github.com/richelbilderbeek/pirouette_example_21}.

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_21/errors_100.png}
  \caption{100 nucleotides}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_21/errors_248.png}
  \caption{248 nucleotides}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_21/errors_500.png}
  \caption{500 nucleotides}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_21/errors_1000.png}
  \caption{1000 nucleotides}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_21/errors_2000.png}
  \caption{2000 nucleotides}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_21/errors_4000.png}
  \caption{4000 nucleotides}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_21/errors_8000.png}
  \caption{8000 nucleotides}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_21/errors_16000.png}
  \caption{16000 nucleotides}
\end{figure}

@@

\richel{Issue at \url{https://github.com/richelbilderbeek/pirouette_article/issues/87}}

@@

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_27/errors.png}
  \caption{An unliked node substitution model}
\end{figure}

@@

\richel{Issue at \url{https://github.com/richelbilderbeek/pirouette_article/issues/68}}

@@

@@

The code used in this part of the article can be found at 
\url{https://github.com/richelbilderbeek/pirouette_example_18}.

@@

@@

The code used in this part of the article can be found at 
\url{https://github.com/richelbilderbeek/pirouette_example_24}.

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_24/errors_1.png}
  \caption{Per-nucleotide mutation rate of 0.0125}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_24/errors_2.png}
  \caption{Per-nucleotide mutation rate of 0.025}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_24/errors_3.png}
  \caption{Per-nucleotide mutation rate of 0.05}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_24/errors_4.png}
  \caption{Per-nucleotide mutation rate of 0.1}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_24/errors_5.png}
  \caption{Per-nucleotide mutation rate of 0.2}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_24/errors_6.png}
  \caption{Per-nucleotide mutation rate of 0.4}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_24/errors_7.png}
  \caption{Per-nucleotide mutation rate of 0.8}
\end{figure}

>>>>

We limited the amount of replicates by time, aiming at a duration of
24 hours per setting, when run on the computer cluster of the
University of Groningen. Due to this, for example, a run of 40 taxa only
has 6 replicates, as one run takes 4 hours.

@@

This subsection extends the main example, by using multiple (instead of
one) trees. These trees are produced by running a DD tree simulation
with the same parameters as the main example.

@@

The main example uses 6 taxa. Here, we show the same results as the main example,
except for a varying number of taxa.

The code used in this part of the article can be found at 
\url{https://github.com/richelbilderbeek/pirouette_example_28} (6 taxa, main example),
\url{https://github.com/richelbilderbeek/pirouette_example_32} (12 taxa),
\url{https://github.com/richelbilderbeek/pirouette_example_33} (24 taxa),
\url{https://github.com/richelbilderbeek/pirouette_example_41} (32 taxa),
\url{https://github.com/richelbilderbeek/pirouette_example_42} (40 taxa).

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_28/errors.png}
  \caption{6 taxa, 16 hours, main example}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_32/errors.png}
  \caption{12 taxa, 19 hours}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_33/errors.png}
  \caption{24 taxa, 28 hours}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_41/errors.png}
  \caption{32 taxa, 7 hours}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_42/errors.png}
  \caption{40 taxa, 8 hours}
\end{figure}

@@

The main example uses a DNA alignment length of 1000 nucleotides.
Here, we show the same results as the main example,
except for a varying DNA alignment sequence length.

The code used in this part of the article can be found at 
\url{https://github.com/richelbilderbeek/pirouette_example_19} (500 nucleotides),
\url{https://github.com/richelbilderbeek/pirouette_example_28} (1000 nucleotides, main example),
and \url{https://github.com/richelbilderbeek/pirouette_example_34} (2000 nucleotides).

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_19/errors.png}
  \caption{500 nucleotides}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_28/errors.png}
  \caption{1000 nucleotides (main example)}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_34/errors.png}
  \caption{2000 nucleotides}
\end{figure}

@@

@@

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_27/errors.png}
  \caption{An unlinked node substitution model, 20 replicates}
\end{figure}

@@

@@

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_23/likelihoods.png}
  \caption{Distribution of likelihoods, as well as which ones are picked}
\end{figure}

@@

The code used in this part of the article can be found at 
\url{https://github.com/richelbilderbeek/pirouette_example_18} and
\url{https://github.com/richelbilderbeek/pirouette_example_28}.

@@

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_28/errors.png}
  \caption{Equal mutation rate and number of mutations (main example)}
\end{figure}

@@

The code used in this part of the article can be found at 
\url{https://github.com/richelbilderbeek/pirouette_example_35} (0.25 / crown age),
\url{https://github.com/richelbilderbeek/pirouette_example_36} (0.50 / crown age),
\url{https://github.com/richelbilderbeek/pirouette_example_37} (0.75 / crown age),
\url{https://github.com/richelbilderbeek/pirouette_example_28} (1.00 / crown age, main example),
\url{https://github.com/richelbilderbeek/pirouette_example_38} (1.25 / crown age),
\url{https://github.com/richelbilderbeek/pirouette_example_39} (1.50 / crown age),
\url{https://github.com/richelbilderbeek/pirouette_example_40} (2.00 / crown age),

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_35/errors.png}
  \caption{Per-nucleotide mutation rate of 0.25 / crown age}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_36/errors.png}
  \caption{Per-nucleotide mutation rate of 0.50 / crown age}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_37/errors.png}
  \caption{Per-nucleotide mutation rate of 0.75 / crown age}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_28/errors.png}
  \caption{Per-nucleotide mutation rate of 1.0 / crown age (main example)}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_38/errors.png}
  \caption{Per-nucleotide mutation rate of 1.25 / crown age}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_39/errors.png}
  \caption{Per-nucleotide mutation rate of 1.50 / crown age}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_40/errors.png}
  \caption{Per-nucleotide mutation rate of 2.0 / crown age}
\end{figure}
